A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-11-19 main.tex
4.2 figure

\anna{Due to the differing sample sizes and subpopulation structures, a direct comparison of the Empirical data, which has a CP $= 0.61$, with those from the simulated data sets is not straightforward. We note that the CP decreases in the presence of subpopulations of unequal sizes and with more outbred subpopulations as is the case in the Empirical data.}

@@

\begin{table}[H]
\centering
\begin{tabularx}{400pt}{cclYYY}
\toprule
$\eta$ & $\xi$ & \multicolumn{1}{c}{Method} & 1D Linear Admixture & Independent Subpopulations & Empirical \\ 
\midrule
\multirow{6}{*}{0.5} & \multirow{3}{*}{0} & lasso & 0.25 (0.05) & 0.23 (0.05) & 0.37 (0.06) \\ 
& & PC-lasso & 0.23 (0.05) & 0.21 (0.05) & 0.36 (0.06) \\ 
& & LMM-lasso & 0.25 (0.05) & 0.23 (0.05) & 0.41 (0.06) \\ 
\cmidrule{2-6}
& \multirow{3}{*}{0.8} & lasso & 0.24 (0.05) & 0.26 (0.06) & 0.29 (0.06) \\
& & PC-lasso & 0.28 (0.05) & 0.36 (0.06) & 0.46 (0.06) \\ 
& & LMM-lasso & 0.28 (0.05) & 0.39 (0.06) & 0.57 (0.05) \\
\bottomrule
\end{tabularx}
\caption{True positive rates, mean (SD), for different data types in the presence and absence of environmental confounding with coarse subpopulation structure and dichotomous-discordant environmental effects.}
\label{tab:var_sel}
\end{table}

@@

% \begin{figure}[H]
%    \centering
%    \includegraphics[scale = 0.9]{figures/mse_diff_hetero.png}
%    \caption{Relative performance of LMM-lasso, PC-lasso for fine and coarse subpopulation structures and varying environmental effect structures with Independent Subpopulations data, $\eta = 0.5$, and $\xi = 0.8$.}
%    \label{fig:big_small_gamma}
%\end{figure}

>>>>

Due to the differing sample sizes and subpopulation structures, a direct comparison of the Empirical data, which has a CP $= 0.87$, with those from the simulated data sets is not straightforward. We note that the CP decreases in the presence of subpopulations of unequal sizes and with more outbred subpopulations as is the case in the Empirical data.

@@

\begin{table}[H]
\centering
\begin{tabularx}{400pt}{cclYYY}
\toprule
$\eta$ & $\xi$ & \multicolumn{1}{c}{Method} & 1D Linear Admixture & Independent Subpopulations & Empirical \\ 
\midrule
\multirow{6}{*}{0.5} & \multirow{3}{*}{0} & lasso & 0.25 (0.05) & 0.23 (0.05) & 0.37 (0.06) \\ 
& & PC-lasso & 0.23 (0.05) & 0.21 (0.05) & 0.36 (0.06) \\ 
& & LMM-lasso & 0.25 (0.05) & 0.23 (0.05) & 0.41 (0.06) \\ 
\cmidrule{2-6}
& \multirow{3}{*}{0.8} & lasso & 0.24 (0.05) & 0.26 (0.06) & 0.29 (0.06) \\ 
& & PC-lasso & 0.28 (0.05) & 0.36 (0.06) & 0.46 (0.06) \\ 
& &  LMM-lasso & 0.28 (0.05) & 0.39 (0.06) & 0.61 (0.06) \\ 
\bottomrule
\end{tabularx}
\caption{True positive rates, mean (SD), for different data types in the presence and absence of environmental confounding with coarse subpopulation structure and dichotomous-discordant environmental effects.}
\label{tab:var_sel}
\end{table}

 \begin{figure}[H]
    \centering
    \includegraphics[scale = 0.9]{figures/popInfSNPs_n=200.png}
    \caption{Causal and non-causal SNP selection in the presence of varying levels of population informative SNPs with a coarse 2 Independent Subpopulation structure, dichotomous-discordant effects, $\eta = 0.5$, and $\xi = 0.8$.}
    \label{fig:big_small_gamma}
\end{figure}

@@
